%%%%%%
% Kiruthika Somasundaram - curriculum vitae
% Edited using emacs and texlive
% Uses LaTeX and moderncv
%%%%%%

\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[grey]{classic}

\usepackage[utf8]{inputenc} % character encoding
\usepackage[scale=0.8]{geometry} % adjust the page margins

\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Kiruthika}
\familyname{Somasundaram}
\address{Melbourne}{Victoria}
\phone{+61-436 420 832}
\email{kiru.somasundaram@gmail.com}
% \photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file;

% --------------------------------------
% CONTENT
% --------------------------------------

\begin{document}
\maketitle

\section{Summary}
\linebreak
\cvlistitem{\textit{AWS Certified Devops Engineer} with 6 years of experience in automation and operations. }
\cvlistitem{Seeking to leverage proven CI/CD skills to design and develop applications in Cloud. }
\cvlistitem{Containerised Tibco microservices in Kubernetes and docker to maintain 99\% availability. }
\cvlistitem{Reduced the turnaround time of support requests by 55\% through ansible and Jenkins orchestration. }
\linebreak
\section {Certification}
\linebreak
\cvlistitem{AWS Certified Solution Architect}
\cvlistitem{Splunk Certified Architect}
\linebreak
\section{Technical skills}
\linebreak
\cvlistitem{\textsc{Infrastructure - }{AWS, Oracle Cloud, Linux, Solaris, Windows} }
\cvlistitem{\textsc{AWS - }{EC2, S3, Cloudformation, SNS, SQS, Firehose, IAM} }
\cvlistitem{\textsc{CI/CD - }{Jenkins, Ansible, Bamboo, Bitbucket, GIT, RTC, Artifactory} }
\cvlistitem{\textsc{Contarization - }{Docker, Kubernetes} }
\cvlistitem{\textsc{Programming - }{Python, Shell, PHP, Javascript, CSS} }
\cvlistitem{\textsc{Monitoring - }{Splunk, Grafana, Prometheus} }
\cvlistitem{\textsc{Ticketing - }{JIRA, BMC Remedy} }
\cvlistitem{\textsc{Server Side Technologies - }{Haproxy} }
\cvlistitem{\textsc{Soft Skills - }{Haproxy} }
\linebreak
\subsection{Soft Skills}
\cvlistitem{Client Engagement, Consulting, Solution Design, Technical Architecture, Collaboration, Stewardship}
% --------------------------------------
% WORK EX
% --------------------------------------

\section{Work Experience and Positions}
\linebreak
\cventry{2017 -- Present}{Accenture Australia}{Devops Engineer/Senior Analyst}{}{}{}
\linebreak
 \cvlistitem{Developing one click deployment using Ansible, Jenkins, Lambda and Aurora which will potentially reduce the service request inflow by 45\%}
 \cvlistitem{Maintaining CI/CD pipeline for 200 users through Jenkins and Git for an Enterprise splunk platform}
 \cvlistitem{Provisioning EC2 instances for various use cases using cloudformation templates.}
 \cvlistitem{Working with SNS, SQS, Firehose to send 80TB of data reliably from AWS S3 to Splunk }

\cvlistitem{Managed tibco microservices running on docker, orchestrated in kubernetes with 99\% availability.}
\cvlistitem{Built automation and monitoring framework using Python, Prometheus, Grafana}
\cvlistitem{Managed CI/CD pipeline in Bamboo and Bitbucket for 6 environments}
\cvlistitem{Proficient in writing yaml for microservices deployments, services and custom access control for the cluster. 
}
\cvlistitem{Worked on server side technology HAproxy to send data securely from an on-premise legacy application to cloud.}
\cvlistitem{Solution design for disaster recovery and fixing application’s security vulnerabilities for a high volume (16k user base) RCRM application. }
\cvlistitem{Managed a team of 3 to build an in-house monitoring solution in Splunk that helps business and other key stakeholders across the platform health. }
\linebreak
\subsection{\textbf{Key Achievements}}
\linebreak
\cvlistitem{Automation jobs resulted in a 55\% decrease in turnaround time for certain service requests. }
\cvlistitem{Client appreciation for excellent product knowledge, hard work, support and dedication while delivering disaster recovery solution for a large scale RCRM application}
\cvlistitem{Managed to resolve critical issues that arose in the kubernetes platform to ensure 99\% availability}
\subsection{}
\cventry{ 2013 - 2017}{Accenture India}{Senior Analyst}{}{}{}
\subsubsection{}
\cvlistitem{Lead technical architect involved in solution design, development of hardware/software upgrade for a Retail-CRM application in Linux, solaris and windows.}
\cvlistitem{Scripted the software upgrade and prerequisite activities in bash which enabled smooth upgradation of 10 environments.}
\cvlistitem{Managed over 20 deployments and service requests in Jenkins, RBF and RTC on a daily basis}
\cvlistitem{Built tools to automate day-to-day tasks in PHP and shell and saved 15 hours of manual efforts per week.}
\cvlistitem{Effectively worked on incident/defect management and capacity assessment for a business critical application used by 16k users.}
\cvlistitem{Worked on integration of Retail-CRM application with LDAP authentication system, Tibco middleware through JMS queues.}
\cvlistitem{Performed Splunk dashboarding for an end to end order tracking system and onboarded data from various downstreams.}
\subsection{}
\subsection{\textbf{Key Achievements}}
\cvlistitem{Appreciated by leadership for environment management and troubleshooting skills}
\cvlistitem{Received various awards from the team for the automation initiatives which resulted in monetary client benefits. }

\section{Education}
\cventry{2009 -- 2013}{Bachelor Of Engineering}{Anna University}{Chennai}{}{}



% --------------------------------------
\end{document}
\end{document}